Master thesis problem statement: Keyword search over heterogeneous sources

### 2012-10-18 doc/thesis/latex/proposed_solutions.tex
slight modifications to report

\subsection{Supporting complex queries}
As most entities in the mediated schema (27 of them) are already mapped to multiple services (see the mapping here: \url{https://cmsweb.cern.ch/das/services}) these taken as a graph could be used to build (some of) the more complex queries.

>>>>

\subsection{Supporting complex queries}
As most entities in the mediated schema (27 of them) are already mapped to multiple services (see the mapping here: \url{https://cmsweb.cern.ch/das/services}) in theory these could be taken as a graph could to build (some of) the more complex queries. {\color{red}At the moment this still needs some further consideration/planning, as the source descriptions we have are not so detailed as for example \textit{Information Manifold's}.}

### 2012-10-18 doc/thesis/latex/report_sept.tex
slight modifications to report

\subsection{Generic connector accessing relational databases}
{\color{red}Generic connector able to access relational databases with minimal manual integration could be useful for integrating proprietary systems that were not yet integrated and there's no resources available to build APIs. A possible use-case could be the \textit{Prep} database, but this still has to be discussed.

Depending on needs it could be either of exploratory or API/Query Forms based approach, where fake APIs are defined in terms of SQL queries (or even better in a simplified form that would generate SQL by taking schema into account)}
+{\color{green} Indeed, an dthat was the topic of research for another DAS student, Liang Dong. The idea was to generalize DBS-QL to any DB back-end and provide common package which will do a job. The work is done over here https://github.com/vkuznet/PyQueryBuilder. Feel free to check it out and we can discuss it more.}
+

>>>>

\subsection{Generic connector accessing relational databases}
{\color{red}Generic connector able to access relational databases with minimal manual integration could be useful for integrating proprietary systems that were not yet integrated and there's no resources available to build APIs. A possible use-case could be the \textit{Prep} database, but this still has to be discussed. 
%
Depending on the needs it could be either of exploratory or API/Query Forms based approach, where fake APIs are defined in terms of SQL queries (or even better in a simplified form that would generate SQL by taking schema into account)}
{
There was a project\footnote{\url{https://github.com/vkuznet/PyQueryBuilder}}   at CERN which tried to generalize DBS-Query Language for any database.}

% \color{green} Indeed, an dthat was the topic of research for another DAS student, Liang Dong. The idea was to generalize DBS-QL to any DB back-end and provide common package which will do a job. The work is done over here . Feel free to check it out and we can discuss it more.}
